Himalayan Expeditions Success Analysis

### 2024-04-18 paper/paper.qmd
Analysis data stored as a parquet

library(broom.mixed)
library(tidyverse)
library(dplyr)
library(knitr)
library(ggplot2)
library(modelsummary)
library(here)
library(kableExtra)

expeditions_model <- readRDS(here("models/single_bay.rds"))
analysis_data <- read.csv(here("data/analysis_data/expeditions.csv"))
```

@@

# Data {#sec-data}
For this analysis, we have used combined three datasets into one, which is used for analysis. The datasets were cleaned and analysed using the statistical programming software `R` [@citeR] along with the help `tidyverse` [@citeTidyverse], `knitr` [@citeKnitr], `ggplot2` [@citeGgplot], `here` [@citeHere], `dplyr` [@citeDplyr], `rstanarm` [@citeRstanarm], `broom.mixed` [@citeBroomMixed], `modelsummary` [@citeModelSummary] and `kableExtra` [@citeKableExtra].

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-model-coefficients
#| tbl-cap: Summary of the model

# Create model summary
# model_summary <- modelsummary(expeditions_model)

@@

@@

# Create a data frame with all combinations of sex and seasons
sex_levels <- unique(analysis_data$sex) 
seasons_levels <- unique(analysis_data$seasons)

new_data <- expand.grid(
  sex = sex_levels,
  seasons = seasons_levels
)

# Predicting success based on sex and seasons
predictions <- predict(expeditions_model, newdata = new_data, type = "response")

# Create a data frame to display the predictions
prediction_df <- data.frame(
  sex = new_data$sex, 
  seasons = new_data$seasons, 
  success_probability = predictions
)

ggplot(prediction_df, aes(x = sex, y = success_probability, fill = sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Predicted Success Probability by Gender",
       x = "Sex",
       y = "Success Probability") +
  theme_minimal()

>>>>

library(broom.mixed)
library(tidyverse)
library(dplyr)
library(knitr)
library(ggplot2)
library(modelsummary)
library(here)
library(kableExtra)
library(arrow)

expeditions_model <- readRDS(here("models/single_bay.rds"))
analysis_data <- read_parquet("data/analysis_data/expeditions.parquet")
predictions <- read.csv(here("data/predictions/predictions.csv"))
```

@@

# Data {#sec-data}
For this analysis, we have used combined three datasets into one, which is used for analysis. The datasets were cleaned and analysed using the statistical programming software `R` [@citeR] along with the help `tidyverse` [@citeTidyverse], `knitr` [@citeKnitr], `ggplot2` [@citeGgplot], `here` [@citeHere], `dplyr` [@citeDplyr], `rstanarm` [@citeRstanarm], `arrow` [@citeArrow], `broom.mixed` [@citeBroomMixed], `modelsummary` [@citeModelSummary] and `kableExtra` [@citeKableExtra].

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-model-coefficients
#| tbl-cap: Summary of the model
# 
# # Create model summary
# model_summary <- modelsummary(expeditions_model)

@@

coefficients <- coefficients[coefficients$term != "age_range81-90", ]

@@

ggplot(predictions, aes(x = sex, y = success_probability, fill = sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Predicted Success Probability by Gender",
       x = "Sex",
       y = "Success Probability") +
  theme_minimal()
